\documentclass[a4paper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

% Minimalist professional theme
\definecolor{primary}{HTML}{2E4053}
\hypersetup{colorlinks=true, urlcolor=primary}

\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

\pagenumbering{gobble}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Pham Hong Minh Tu}} \\
    \medskip
    \href{mailto:pminhtu787@gmail.com}{pminhtu787@gmail.com} \ $|$ \ (+84) 793 823 787 \ $|$ \ Ho Chi Minh City, Vietnam \\
    \href{https://linkedin.com/in/tu-pham-264065319/}{linkedin.com/in/tu-pham-264065319} \ $|$ \ \href{https://github.com/BlueWhaleo5}{github.com/BlueWhaleo5}
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section{Summary}
Dynamic 3rd-year Computer Engineering student with a strong foundation in Data Engineering and Machine Learning. Passionate about transforming complex data streams into actionable marketing insights and customer-centric AI solutions. Proven leadership through club presidency and a researcher assistant background in AIoT.

% --- EDUCATION ---
\section{Education}
\textbf{Ho Chi Minh City University of Technology (BKU - HCMUT)} \hfill Sep 2023 -- Present \\
Bachelor of Engineering in Computer Engineering (3rd Year) \\
\begin{itemize}
    \item Relevant Coursework: Data Structures \& Algorithms, Database Systems, Machine Learning, Big Data Processing, Cloud Computing, Advanced Programming with Python.
    \item Member of Institute of Advanced Interdisciplinary Science and Technology.
    \item Research Assistant in AIoT and Quantum Computing at BKCPS Laboratory.
\end{itemize}

% --- SKILLS ---
\section{Skills}
\begin{itemize}
    \item \textbf{Data Engineering:} PySpark, Apache Kafka, MinIO, Trino, ETL/ELT Pipeline Development.
    \item \textbf{Machine Learning \& Analytics:} Natural Language Processing (NLP), Regression Analysis, Exploratory Data Analysis (EDA), Statistical Modeling, Scikit-learn, Pandas.
    \item \textbf{Tools \& Infrastructure:} Kubernetes, Docker, SQL, Jupyter Notebook, Git, LaTeX.
    \item \textbf{Soft Skills:} Strategic Leadership, Creative Communication, Stakeholder Management, Adaptability.
\end{itemize}

% --- PROJECTS ---
\section{Key Projects}

\textbf{Smart Dev-Docs Platform} \hfill \href{https://github.com/BlueWhaleo5/Smart_Dev_Cloud_Native}{GitHub Link} \\
\textit{Technologies: Kubernetes, Kafka, Spark Streaming, Iceberg, Qdrant, Ollama, Groq}
\begin{itemize}
    \item Architected a cloud-native RAG platform on Kubernetes for automated technical documentation processing.
    \item Built an event-driven data pipeline using Kafka and Spark Streaming to archive document chunks into an Iceberg Lakehouse.
    \item Developed a Tech Blog Summary system using Llama-3 (Groq API) to extract concise technical insights.
    \item \textbf{AI Optimization:} Fine-tuned RAG retrieval logic and system prompts to enhance chatbot accuracy for developer-centric queries.
\end{itemize}

\textbf{Smart Consumer Complaint Resolution Assistant} \hfill \href{https://github.com/BlueWhaleo5/Smart-Consumer-Complaint-Resolution-Assistant}{GitHub Link} \\
\textit{Technologies: Python, Scikit-learn, LangChain, Gemini/Llama-3, Streamlit}
\begin{itemize}
    \item Architected an end-to-end AI platform using \textbf{Random Forest} and \textbf{TF-IDF} to classify complaint categories and prioritize high-severity cases from a \textbf{7.4GB} dataset (1.3M+ records).
    \item Integrated a \textbf{Retrieval-Augmented Generation (RAG)} assistant using \textbf{LangChain}, enabling staff to query internal policy documents and historical case resolutions with low-latency response times.
    \item Developed a real-time \textbf{Streamlit dashboard} for automated \textbf{EDA}, transforming complex raw data into actionable visual insights regarding product trends and seasonal anomalies.
    \item \textbf{Impact:} Bridged technical AI modeling with business needs, providing a scalable solution for automated customer sentiment tracking and retention optimization.
\end{itemize}

\textbf{IoT Data Streaming & Analytics Platform} \hfill \href{https://github.com/BlueWhaleo5/IOT-Data-Streaming-Platform}{GitHub Link} \\
\textit{Technologies: PySpark, Kafka, MinIO, Trino, Python}
\begin{itemize}
    \item Built a real-time data pipeline to process high-velocity IoT streams for anomaly detection and predictive maintenance.
    \item Designed a scalable storage layer and efficient query interface using Trino and MinIO.
\end{itemize}

% --- LEADERSHIP & ACTIVITIES ---
\section{Leadership \& Activities}
\textbf{President of Volunteer Club} \hfill Sep 2024 -- 2025
\begin{itemize}
    \item Managing a team of 50+ members to organize community projects and social events.
    \item Coordinating with external partners and sponsors, enhancing negotiation and organizational skills.
\end{itemize}

\textbf{Freelance Photographer} \hfill 2023 -- Present
\begin{itemize}
    \item Collaborating with diverse clients to deliver high-quality visual content.
    \item Developing a "marketing-ready" eye for detail and strong interpersonal communication skills.
\end{itemize}

% --- CERTIFICATES & LANGUAGES ---
\section{Certificates \& Languages}
\begin{itemize}
    \item \textbf{English:} IELTS Certificate (B2).
    \item \textbf{German:} Currently learning (A1).
\end{itemize}

\end{document}
